Draft-assinment1

### 2017-02-21 Draft-xuezhou-sjb.Rmd

#2. Goal<a id="Goal"></a>
College is an investment. It's well-known that a major motivation for students to attend a university is higher post-graduation earning. So will your school make sure you get a return? With collge costs and student-debt levels reaching an all-time high, it's important to know which schools produce the highest earning alumni and what factors can help us predict post-graduate earnings for students in a university.

@@

@@

As a result of all the statistical analysis, we conclude that XXXXXXXXXXXX. Attributes such as                will affec the students' post graudate earnings.

>>>>

#2. Goal<a id="Goal"></a>

College is an investment. It's well-known that a major motivation for students to attend a university is higher post-graduation earning. So will your school make sure you get a return? With collge costs and student-debt levels reaching an all-time high, it's important to know which schools produce the highest earning alumni and what factors can help us predict post-graduate earnings for students in a university.

@@

We also found that California has the most universities across the nation, with 797 institutions. In terms of predominant degree offered, 43.2% are classified as Certificate-degree predominant institution, which is the most predominant type.

@@

As to the factors that influence post-graduate earning, we explore the relationship between median earning six years from entry and amount of debt, default rate for student loan and predominant degree type. The analysis suggests that there is a positive relationship between the median debt amount for students who have not completed and post-graduation earnings. This may be due to the fact that top universities usually have tuitions but may also indicates that students who are willing to take more debts for their college education are likely to make more money after graduation. In addition, default rate of student loan is negatively related to post-graduate earning. This finding is reasonable since students making more money are more likely to pay off their debt. The variable can be used a school-level predictor to predict overall post-graduate earning for each university. The degree type, unsurprisingly, has an impact on the earnings students are making after graduation. As the level of graduation increases, the post-graduate earning also increase significantly, which suggests that investing in education is worthwhile.

As a result of all the statistical analysis, we conclude that XXXXXXXXXXXX. Attributes such as               the students' post graudate earnings.
